---
title: "Health Expenditures from 1995 to 2010"
author: "William W. Chiang"
date: "December 28, 2015"
output: html_document
---

##Read health data
```{r}
health <- read.csv('indicator_government_health_spending1.csv')
```


##Rename column labels
```{r}
colnames(health) <- c("Country", 1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010)
```


##Install reshape2 package used to reshape the health data frame
```{r}
library(reshape2)
reshaped_health <- melt(health)
colnames(reshaped_health) <- c("Country", "Year", "Cost")
```


##Create plot of the change in healthcare expenditures over time for the United States, United Kingdom, Canada, Germany, and France
```{r}
library(ggplot2)
ggplot(reshaped_health, aes(x = Year, y = Cost, color = Country)) +
  geom_point(data = subset(reshaped_health, Country %in% c("United States", "United Kingdom", "Canada", "Germany","France")), size = 3) +
  ggtitle("Total Government Healthcare Expenditures from 1995 to 2010")
```


##Save the plot created
```{r}
ggsave('point_graph_healthExpenditures.png')
```


##Overview
In summary, both Canada and the United States have seen a steady rise in healthcare expenditures from the years 1995 to 2007. The United States, in particular, had a sharp rise approaching 2010, which may be attributed to the passage of the Affordable Care Act of 2010.
