---
title: "Udacity Problem Set 3"
author: "William W. Chiang"
date: "December 25, 2015"
output: html_document
---

Lesson 3
========================================================

***

### Diamonds Data
Notes: Prices of 50,000 round cut diamonds

Description

A dataset containing the prices and other attributes of almost 54,000 diamonds. The variables are as follows:

Usage

data(diamonds)
Format

A data frame with 53940 rows and 10 variables

Details

price. price in US dollars (\$326–\$18,823)

carat. weight of the diamond (0.2–5.01)

cut. quality of the cut (Fair, Good, Very Good, Premium, Ideal)

colour. diamond colour, from J (worst) to D (best)

clarity. a measurement of how clear the diamond is (I1 (worst), SI1, SI2, VS1, VS2, VVS1, VVS2, IF (best))

x. length in mm (0–10.74)

y. width in mm (0–58.9)

z. depth in mm (0–31.8)

depth. total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43–79)

table. width of top of diamond relative to widest point (43–95)

***


##1
Load ggplot2 package and 'diamonds' data set and print summary
```{r}
library(ggplot2)
data(diamonds)
summary(diamonds)
```

***

##2
Create a histogram of the price of all the diamonds in the diamond data set
```{r}
qplot(x = price, data = diamonds)
```
Shape is right-skewed

```{r}
summary(diamonds$price)
```
Mean (3933) is more on the right than the median (2401)

***

##3
# Number of diamonds costing less than $500
```{r}
dim(subset(diamonds, price < 500))
```

# Number of diamonds costing less than $250
```{r}
dim(subset(diamonds, price < 250))
```

# Number of diamonds costing $15,000 *or* more
```{r}
dim(subset(diamonds, price >= 15000))
```

***

##4
#Explore the largest peak in the price histogram

```{r}
qplot(x = price, data = diamonds, color = I('black'), fill = I('#009999'), binwidth = 25) +
  scale_x_continuous(limits= c(0,2500), breaks = seq(0,2400,200))
```

Most common price of diamond is in the range of $600 - $800

***

##5

#Break out the histogram of diamond prices by cut
```{r}
qplot(x = price, data = diamonds, color = I('black'), fill = I('#009999'), binwidth = 500) +
  facet_wrap(~cut)
```

Determine which cut has (1) the highest priced diamond, (2) the lowest priced diamond, and (3) the lowest median price
```{r}
by(diamonds$price,diamonds$cut,summary, digits = max(getOption('digits')))
```

***

##6
Like the previous qplot code but with added facet_wrap parameter implemented so that the y-axis in the histogram is not fixed
```{r}
qplot(x = price, data = diamonds, color = I('black'), fill = I('#009999'), binwidth = 500) +
  facet_wrap(~cut, scales = "free_y")
```
***

***
##7
###Create a histogram of price per carat and facet it by cut
```{r}
qplot(x = price/carat, data = diamonds, color = I('black'), fill = I('#009999'), binwidth = 500) +
  facet_wrap(~cut, scales = "free_y")
```

###Adjust the bin width and transform the scale of the x-axis using log10
```{r}
qplot(x = log10(price/carat), data = diamonds, color = I('black'), fill = I('#009999'), binwidth = 0.05) + 
  facet_wrap(~cut, scales = "free_y")
```
***

##8

###Investigate the price of diamonds using box plots, numerical summaries, and one of the following categorical variables: cut, clarity, or color

##BOX PLOT - by cut
```{r}
qplot(x = cut, y = price, data = diamonds, geom = "boxplot") +
  coord_cartesian(ylim = c(0, 7000))
```

##BOX PLOT - by clarity
```{r}
qplot(x = clarity, y = price, data = diamonds, geom = "boxplot") +
  coord_cartesian(ylim = c(0, 7000))
```

##BOX PLOT - by color
```{r}
qplot(x = color, y = price, data = diamonds, geom = "boxplot") +
  coord_cartesian(ylim = c(0, 8000))
```

##Numerical summaries
```{r}
by(diamonds$price, diamonds$color, summary)
```

***

##9

# Boxplot illustrating the price per carat of diamonds across the different colors of diamonds
```{r}
qplot(x = color, y = price/carat, data = diamonds, geom = "boxplot")
```

***

##10
### Illustration of a frequencies polygon according to carats of diamonds
```{r}
qplot(x = carat,
      data = diamonds,
      binwidth = 0.01,
      geom = 'freqpoly') +
  scale_x_continuous(lim = c(0,3), breaks = seq(0,3,0.3))
```

***
